---
title: "Height Income, Arbeidskrav 2 MSB104"
author: "Anne Grete Lilleland, Arian Steen"
date: "8 10 2020"
output: html_document
---

```{r}
library(citr)
library(tinytex)
library(knitr)
library(ggplot2)
library(tidyverse)
library(modelr)
library(ggpubr)
library(dplyr)
```

## Introduction

It has been claimed that the height of a person is one of the most deciding factors for the persons income. In this short paper we will investigate this assertion by using a dataset from the _National Longitudinal Study_ (U.S. Bureau of Labor Statistics). See `help(heights, package = modelr)`for details.

## Summary statistics

We start by grouping the heights in 8 intervals and report summary statistics.

```{r}
heights$heightInt <-cut(heights$height, breaks = 8)
kable(summary(heights[,1:4]))
kable(summary(heights[,5:9]))
```

<<<<<<< HEAD
=======
## Plots

```{r plot-height-income,  out.width="50%"}
ggplot(heights, mapping = aes(x = height, y = income))+
  geom_point()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = heightInt, y = income)) +  scale_y_continuous(trans = scales::log_trans()) +  geom_boxplot()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height, y = income)) +  scale_y_continuous(trans = scales::log_trans()) +  geom_point(position = "jitter") +  geom_smooth(method = 'lm')
```


```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = heigh, y = income)) +  geom_point(position = "jitter") +  geom_smooth(method = 'lm')
```

##How much do we earn extra per inch

>>>>>>> 7c4b83d4c9ba525bb38c05a250e8648d63b708e1




